Union and intersection contracts are hard, actually

### 2021-07-25 paper.tex
Revision: user-defined contracts compatibility

However appealing union and intersection contracts may be, they happen
to be fundamentally incompatible with the desirable language
features from Section~\ref{sec:feat-lang}. At least in their
full-blown form: in Section~\ref{sec:issues-literature} we will
discuss pragmatic restrictions of union and intersection contracts to
recover some or all of the features.

@@

The algorithmic system of~\cite{KeilThiemannUnionIntersection} is, on
balance, a technically impressive realization of the coinductive
semantics, though it is fairly complex and probably difficult to
implement efficiently.

>>>>

However appealing union and intersection contracts may be, they happen to be
either hard to combine or even fundamentally incompatible with the desirable
language features from Section~\ref{sec:feat-lang}. At least in their full-blown
form: in Section~\ref{sec:issues-literature} we will discuss pragmatic
restrictions of union and intersection contracts to recover some or all of the
features.

@@

The algorithmic system of~\cite{KeilThiemannUnionIntersection} is, on balance, a
technically impressive realization of the coinductive semantics that supports
user-defined contracts, though it is fairly complex and probably difficult to
implement efficiently.
